Solving a probabilistic planning problem by presenting a history in the field of probabilistic planning

### 2014-04-13 FinalPaper/paper.tex
Adding communication protocol of UAVs to domain evaluation

>>>>

Dead ends can be avoided in the \textsc{Navigation} domain by adding actions
with a high cost. If a handshake protocol is added to the UAV communication,
the sending UAV knows if the transmission failed and initiate another
transmission of the message until it received an acknowledgement. This takes
more time but it avoids dead ends in the UAV domain.
